%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Officer} % Job title
    {Armed Conflict Location and Events Data Project (ACLED)} % Organization
    {Remote} % Location
    {April 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed external R and Python packages for the organization, aimed at data gathering, data cleaning, and data analysis.}
        \item {Developed the internal R packages of the organization, designed its unit tests, and implemented its CI/CD pipelines.} % summarise this and the first point in one
        \item {Developed CI/CD pipelines for the deployment of internal production-critical applications, reducing the time to deploy significantly and without manual intervention.}
        \item {Acted as the main point of contact for the organization's data team cybersecurity concerns, creating protocols and implementing tools such as organization-wide secrets for efficient.}
        \item {Deployed the organization's Apache Airflow server and provided traininng on creating DAGs and ETL pipelines, as well as designed a suite of tools to support non-python users with DAGs creation.}
        \item {Designed and implemented the data team's github infrastructure, centralizing our team's repositories and optimizing existing workflows through CI/CD pipelines and structured code reviews.}
        \item {Implemented multiple Data Engineering and Data Management trainings for a wide range of staff across the organization.}
        \item {Developed dashboards and ETL pipelines to support other teams in the organization, such as Business Intelligence units and Communications units.}
        \item {Created web applications to deploy our data and analysis, including the use of Shiny, Quarto and Jupyter notebooks.}
        \item {Created documentation for a variety of projects and external-facing applications.}
        \item {Optimized multiple data management scripts, including the usage of Bash, SQL, R and Python, transforming manual and interactive scripts into automatized ETL pipelines.}
        \item {Managed different aspects of the data team's cloud infrastructure, primarely in DigitalOceans, including setting up new servers, managing networking, and troubleshooting problems across droplets.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {International Research Fellow} % Job title
    {Caucasus Research Resource Center (CRRC)} % Organization
    {Tbilisi, Georgia} % Location
    {August 2021 - May 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Gathered and analysed large datasets on official diplomatic communications and social media data, including the use of quantitative text models (supervised and unsupervised classification models).}
        \item {Assisted in the analysis and development of quantitative research projects in digital disinformation, and strategic developments in Georgia, including the use of regression and clustering models.}
        \item {Assisted in the implementation and design of multiple nation-wide surveys for international organizations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Assistant Analyst} % Job title
    {The Hague Centre for Strategic Studies (HCSS)} % Organization
    {The Hague, Netherlands} % Location
    {August 2019 - February 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-authored and contributed to reports in national security planning, hybrid threats and strategic foresight. While also providing assistance in projects regarding multi-domain operations, interstate military conflict and security sector reform.}
        \item {Strengthened and drafted the research design of several projects along the lines of security sector reform, hybrid threats, national security planning and strategic foresight.}
        \item {Prepared ETL pipelines and visualizations through Tableau, Tableau Prep and SQL, combining datasets from different sources and utilizing them to support research projects at the think tank.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
